---
title: "weightedBayes"
author: "Kristian Severin"
date: "2023-05-27"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
# loading packages
pacman::p_load(  
  tidyverse,
  brms,
  cmdstanr,
  patchwork,
  future, 
  purrr, 
  furrr,
  bayesplot,
  drc,
  ggpubr
  )

source("Functions/weightedBayes_f.R")  # get self-written function used to simulate data with
source("Functions/priorSensW_f.R")  # get self-written function for prior sensitivity analysis

```

```{r}
# set up experimental setup
nskiers <- 10
bias <- seq(0.1,0.9, 0.1)
trials <- seq(10)
Source1 <- seq(0.1,0.9, 0.1)
Source2 <- seq(0.1,0.9, 0.1)
w1 <- seq(0.5, 1, 0.1)
w2 <- seq(0.5, 1, 0.1)

db <- expand.grid(bias = bias, trials, Source1 = Source1, Source2 = Source2, w1 = w1, w2 = w2)

for (n in seq(nrow(db))) {  # use weighted bayes logic
  db$beliefAssessment[n] <- WeightedBayes_f(db$bias[n], db$Source1[n], db$Source2[n],db$w1[n], db$w2[n])  
 
  db$outcome[n] <- rbinom(1,1, db$beliefAssessment[n])
 
  db$continuous[n] <- db$beliefAssessment[n] * 11
 
  db$discrete[n] <- round(db$beliefAssessment[n] * 11,0)
 
}

db <- rename(db, "skier" = "Var2") 

# make the dataset feasible for fitting 
db <- sample_n(db, size = 26244)

# omit NA's
db <- db %>% na.omit()
```


```{r}
# pivot data wider
sim_wide_weighted <- db %>% 
  group_by(skier) %>% 
  subset(select = c(skier, outcome, Source1, Source2, bias)) %>%
  mutate(row = row_number()) %>% 
  pivot_wider(names_from = skier, values_from = c(outcome, Source1, Source2, bias))

sim_wide_weighted <- sim_wide_weighted %>% na.omit()

# Create the data
dataWeightedBayes <- list(
  N = nrow(sim_wide_weighted),
  S = nskiers,
  outcome = as.matrix(sim_wide_weighted[,2:11]),
  Source1 = as.matrix(sim_wide_weighted[,12:21]),
  Source2 = as.matrix(sim_wide_weighted[,22:31]),
  bias = as.matrix(sim_wide_weighted[,32:41])
)

# feed R the stan model
file <- file.path("weightedBayes.stan")
mod_WeightedBayes <- cmdstan_model(file, cpp_options = list(stan_threads = TRUE),
                     stanc_options = list("O1"))
# create samples from the model
samples_weighted <- mod_WeightedBayes$sample(
  data = dataWeightedBayes,
  seed = 123,
  chains = 2,
  parallel_chains = 2,
  threads_per_chain = 2,
  iter_warmup = 1500,
  iter_sampling = 3000,
  refresh = 500,
  max_treedepth = 10
)

# get the resulting data frame
draws_df_weighted <- as_draws_df(samples_weighted$draws())
```

This chunk has all the prior and posterior predictive checks
```{r}
# prior predictive plots
Prior_predictive_checks_pb <- 
ggplot(draws_df_weighted) +
  geom_histogram(aes(`prior_predsb5[1]`), color = "yellow", fill = "lightyellow", alpha = 0.2) +
    annotate("text",  x = 340, y = 2100, label = "*0.5-Adjusted Prior" , hjust = 0)+
  geom_histogram(aes(`prior_predsb7[1]`), color = "green", fill = "lightgreen", alpha = 0.2) +
    annotate("text",  x = 450, y = 900, label = "*0.7-Adjusted Prior" , hjust = 0)+
  geom_histogram(aes(`prior_predsb9[1]`), color = "blue", fill = "lightblue", alpha = 0.2) +
    annotate("text",  x = 550, y = 600, label = "*0.9-Adjusted Prior" , hjust = 0)+
  xlab("Predicted skied runs out of 729") +
  ylab("Posterior Density") +
  ggtitle("Prior Predictive Checks")+
  theme_classic()

Prior_predictive_checks_pw1 <- 
ggplot(draws_df_weighted) +
  geom_histogram(aes(`prior_predsw15[1]`), color = "yellow", fill = "lightyellow", alpha = 0.2) +
    annotate("text",  x = 340, y = 2100, label = "*0.5-Adjusted Prior" , hjust = 0)+
  geom_histogram(aes(`prior_predsw17[1]`), color = "green", fill = "lightgreen", alpha = 0.2) +
    annotate("text",  x = 450, y = 900, label = "*0.7-Adjusted Prior" , hjust = 0)+
  geom_histogram(aes(`prior_predsw19[1]`), color = "blue", fill = "lightblue", alpha = 0.2) +
    annotate("text",  x = 550, y = 600, label = "*0.9-Adjusted Prior" , hjust = 0)+
  xlab("Predicted skied runs out of 729") +
  ylab("Posterior Density") +
  ggtitle("Prior Predictive Checks")+
  theme_classic()

Prior_predictive_checks_pw2 <- 
ggplot(draws_df_weighted) +
  geom_histogram(aes(`prior_predsw25[1]`), color = "yellow", fill = "lightyellow", alpha = 0.2) +
    annotate("text",  x = 340, y = 2100, label = "*0.5-Adjusted Prior" , hjust = 0)+
  geom_histogram(aes(`prior_predsw27[1]`), color = "green", fill = "lightgreen", alpha = 0.2) +
    annotate("text",  x = 450, y = 900, label = "*0.7-Adjusted Prior" , hjust = 0)+
  geom_histogram(aes(`prior_predsw29[1]`), color = "blue", fill = "lightblue", alpha = 0.2) +
    annotate("text",  x = 550, y = 600, label = "*0.9-Adjusted Prior" , hjust = 0)+
  xlab("Predicted skied runs out of 729") +
  ylab("Posterior Density") +
  ggtitle("Prior Predictive Checks")+
  theme_classic()


post_predictive_checks_pb <- 
ggplot(draws_df_weighted) +
  geom_histogram(aes(`post_predsb5[1]`), color = "yellow", fill = "lightyellow", alpha = 0.2) +
    annotate("text",  x = 340, y = 2100, label = "*0.5-Adjusted Prior" , hjust = 0)+
  geom_histogram(aes(`post_predsb7[1]`), color = "green", fill = "lightgreen", alpha = 0.2) +
    annotate("text",  x = 450, y = 900, label = "*0.7-Adjusted Prior" , hjust = 0)+
  geom_histogram(aes(`post_predsb9[1]`), color = "blue", fill = "lightblue", alpha = 0.2) +
    annotate("text",  x = 550, y = 600, label = "*0.9-Adjusted Prior" , hjust = 0)+
  xlab("Predicted skied runs out of 729") +
  ylab("Posterior Density") +
  ggtitle("Prior Predictive Checks")+
  theme_classic()

post_predictive_checks_pw1 <- 
ggplot(draws_df_weighted) +
  geom_histogram(aes(`post_predsw15[1]`), color = "yellow", fill = "lightyellow", alpha = 0.2) +
    annotate("text",  x = 340, y = 2100, label = "*0.5-Adjusted Prior" , hjust = 0)+
  geom_histogram(aes(`post_predsw17[1]`), color = "green", fill = "lightgreen", alpha = 0.2) +
    annotate("text",  x = 450, y = 900, label = "*0.7-Adjusted Prior" , hjust = 0)+
  geom_histogram(aes(`post_predsw19[1]`), color = "blue", fill = "lightblue", alpha = 0.2) +
    annotate("text",  x = 550, y = 600, label = "*0.9-Adjusted Prior" , hjust = 0)+
  xlab("Predicted skied runs out of 729") +
  ylab("Posterior Density") +
  ggtitle("Prior Predictive Checks")+
  theme_classic()

post_predictive_checks_pw2 <- 
ggplot(draws_df_weighted) +
  geom_histogram(aes(`post_predsw25[1]`), color = "yellow", fill = "lightyellow", alpha = 0.2) +
    annotate("text",  x = 340, y = 2100, label = "*0.5-Adjusted Prior" , hjust = 0)+
  geom_histogram(aes(`post_predsw27[1]`), color = "green", fill = "lightgreen", alpha = 0.2) +
    annotate("text",  x = 450, y = 900, label = "*0.7-Adjusted Prior" , hjust = 0)+
  geom_histogram(aes(`post_predsw29[1]`), color = "blue", fill = "lightblue", alpha = 0.2) +
    annotate("text",  x = 550, y = 600, label = "*0.9-Adjusted Prior" , hjust = 0)+
  xlab("Predicted skied runs out of 729") +
  ylab("Posterior Density") +
  ggtitle("Prior Predictive Checks")+
  theme_classic()

both_b5 <- ggplot(draws_df_weighted) +
  geom_histogram(aes(`prior_predsb5[1]`), color = "lightyellow", fill = "yellow", alpha = 0.3, bins = 90) +
  geom_histogram(aes(`post_predsb5[1]`), color = "#666600", fill = "yellow", alpha = 0.3, bins = 90) +
  xlab("Predicted skied runs out of 2527 trials") +
  ylab("Posterior Density") +
  ggtitle("β 0.5 adjusted prior")+
  theme_classic()


both_w15 <- ggplot(draws_df_weighted) +
  geom_histogram(aes(`prior_predsw15[1]`), color = "lightyellow", fill = "yellow", alpha = 0.3, bins = 90) +
  geom_histogram(aes(`post_predsw15[1]`), color = "#666600", fill = "yellow", alpha = 0.3, bins = 90) +
  xlab("Predicted skied runs out of 2527 trials") +
  ylab("Posterior Density") +
  ggtitle("ω1 0.5 adjusted prior")+
  theme_classic()

both_w25 <- ggplot(draws_df_weighted) +
  geom_histogram(aes(`prior_predsw25[1]`), color = "lightyellow", fill = "yellow", alpha = 0.3, bins = 90) +
  geom_histogram(aes(`post_predsw25[1]`), color = "#666600", fill = "yellow", alpha = 0.3, bins = 90) +
  xlab("Predicted skied runs out of 2527 trials") +
  ylab("Posterior Density") +
  ggtitle("ω2 0.5 adjusted prior")+
  theme_classic()

both_b7 <- ggplot(draws_df_weighted) +
  geom_histogram(aes(`prior_predsb7[1]`), color = "lightgreen", fill = "green", alpha = 0.3, bins = 90) +
  geom_histogram(aes(`post_predsb7[1]`), color = "darkgreen", fill = "green", alpha = 0.3, bins = 90) +
  xlab("Predicted skied runs out of 2527 trials") +
  ylab("Posterior Density") +
  ggtitle("β 0.7 adjusted prior")+
  theme_classic()


both_w17 <- ggplot(draws_df_weighted) +
  geom_histogram(aes(`prior_predsw17[1]`), color = "lightgreen", fill = "green", alpha = 0.3, bins = 90) +
  geom_histogram(aes(`post_predsw17[1]`), color = "darkgreen", fill = "green", alpha = 0.3, bins = 90) +
  xlab("Predicted skied runs out of 2527 trials") +
  ylab("Posterior Density") +
  ggtitle("ω1 0.7 adjusted prior")+
  theme_classic()

both_w27 <- ggplot(draws_df_weighted) +
  geom_histogram(aes(`prior_predsw27[1]`), color = "lightgreen", fill = "green", alpha = 0.3, bins = 90) +
  geom_histogram(aes(`post_predsw27[1]`), color = "darkgreen", fill = "green", alpha = 0.3, bins = 90) +
  xlab("Predicted skied runs out of 2527 trials") +
  ylab("Posterior Density") +
  ggtitle("ω2 0.7 adjusted prior")+
  theme_classic()

both_b9 <- ggplot(draws_df_weighted) +
  geom_histogram(aes(`prior_predsb9[1]`), color = "lightblue", fill = "blue", alpha = 0.3, bins = 90) +
  geom_histogram(aes(`post_predsb9[1]`), color = "darkblue", fill = "blue", alpha = 0.3, bins = 90) +
  xlab("Predicted skied runs out of 2527 trials") +
  ylab("Posterior Density") +
  ggtitle("β 0.9 adjusted prior")+
  theme_classic()


both_w19 <- ggplot(draws_df_weighted) +
  geom_histogram(aes(`prior_predsw19[1]`), color = "lightblue", fill = "blue", alpha = 0.3, bins = 90) +
  geom_histogram(aes(`post_predsw19[1]`), color = "darkblue", fill = "blue", alpha = 0.3, bins = 90) +
  xlab("Predicted skied runs out of 2527 trials") +
  ylab("Posterior Density") +
  ggtitle("ω1 0.9 adjusted prior")+
  theme_classic()

both_w29 <- ggplot(draws_df_weighted) +
  geom_histogram(aes(`prior_predsw29[1]`), color = "lightblue", fill = "blue", alpha = 0.3, bins = 90) +
  geom_histogram(aes(`post_predsw29[1]`), color = "darkblue", fill = "blue", alpha = 0.3, bins = 90) +
  xlab("Predicted skied runs out of 2527 trials") +
  ylab("Posterior Density") +
  ggtitle("ω2 0.9 adjusted prior")+
  theme_classic()

Prior_predictive_checks_pb
Prior_predictive_checks_pw1
Prior_predictive_checks_pw2

post_predictive_checks_pb
post_predictive_checks_pw1
post_predictive_checks_pw2

both_b5+both_b7+both_b9+both_w15+both_w17+both_w19+both_w25+both_w27+both_w29 + plot_annotation(title = "Prior and Posterior Predictive Checks", subtitle = "Weighted Bayes Model Parameters")
```


This chunk has all the prior posterior update plots for bias
```{r}
### prior posterior update plots for bias  ###
# bias plot
b1w <- ggplot(draws_df_weighted) +
  geom_density(aes(`bias_posterior[1]`), alpha = 0.6, fill = "lightblue") +
  geom_density(aes(`bias_prior[1]`), alpha = 0.6, fill = "pink") +
  xlab("Bias")+
  ylab("Estimate Densitites")+
  theme_bw()+
  geom_vline(xintercept = median(db$bias), linetype = "dashed", size = 1.5) +
  ggtitle("Simulated Skier 1")

# bias plot
b2w <- ggplot(draws_df_weighted) +
  geom_density(aes(`bias_posterior[2]`), alpha = 0.6, fill = "lightblue") +
  geom_density(aes(`bias_prior[2]`), alpha = 0.6, fill = "pink") +
  xlab("Bias")+
  ylab("Estimate Densitites")+
  theme_bw()+
  geom_vline(xintercept = median(db$bias), linetype = "dashed", size = 1.5) +
  ggtitle("Simulated Skier 2")

# bias plot
b3w <- ggplot(draws_df_weighted) +
  geom_density(aes(`bias_posterior[3]`), alpha = 0.6, fill = "lightblue") +
  geom_density(aes(`bias_prior[3]`), alpha = 0.6, fill = "pink") +
  xlab("Bias")+
  ylab("Estimate Densitites")+
  theme_bw()+
  geom_vline(xintercept = median(db$bias), linetype = "dashed", size = 1.5) +
  ggtitle("Simulated Skier 3")

# bias plot
b4w <- ggplot(draws_df_weighted) +
  geom_density(aes(`bias_posterior[4]`), alpha = 0.6, fill = "lightblue") +
  geom_density(aes(`bias_prior[4]`), alpha = 0.6, fill = "pink") +
  xlab("Bias")+
  ylab("Estimate Densitites")+
  theme_bw()+
  geom_vline(xintercept = median(db$bias), linetype = "dashed", size = 1.5) +
  ggtitle("Simulated Skier 4")

# bias plot
b5w <- ggplot(draws_df_weighted) +
  geom_density(aes(`bias_posterior[5]`), alpha = 0.6, fill = "lightblue") +
  geom_density(aes(`bias_prior[5]`), alpha = 0.6, fill = "pink") +
  xlab("Bias")+
  ylab("Estimate Densitites")+
  theme_bw()+
  geom_vline(xintercept = median(db$bias), linetype = "dashed", size = 1.5) +
  ggtitle("Simulated Skier 5")

# bias plot
b6w <- ggplot(draws_df_weighted) +
  geom_density(aes(`bias_posterior[6]`), alpha = 0.6, fill = "lightblue") +
  geom_density(aes(`bias_prior[6]`), alpha = 0.6, fill = "pink") +
  xlab("Bias")+
  ylab("Estimate Densitites")+
  theme_bw()+
  geom_vline(xintercept = median(db$bias), linetype = "dashed", size = 1.5) +
  ggtitle("Simulated Skier 6")

# bias plot
b7w <- ggplot(draws_df_weighted) +
  geom_density(aes(`bias_posterior[7]`), alpha = 0.6, fill = "lightblue") +
  geom_density(aes(`bias_prior[7]`), alpha = 0.6, fill = "pink") +
  xlab("Bias")+
  ylab("Estimate Densitites")+
  theme_bw()+
  geom_vline(xintercept = median(db$bias), linetype = "dashed", size = 1.5) +
  ggtitle("Simulated Skier 7")

# bias plot
b8w <- ggplot(draws_df_weighted) +
  geom_density(aes(`bias_posterior[8]`), alpha = 0.6, fill = "lightblue") +
  geom_density(aes(`bias_prior[8]`), alpha = 0.6, fill = "pink") +
  xlab("Bias")+
  ylab("Estimate Densitites")+
  theme_bw()+
  geom_vline(xintercept = median(db$bias), linetype = "dashed", size = 1.5) +
  ggtitle("Simulated Skier 8")

# bias plot
b9w <- ggplot(draws_df_weighted) +
  geom_density(aes(`bias_posterior[9]`), alpha = 0.6, fill = "lightblue") +
  geom_density(aes(`bias_prior[9]`), alpha = 0.6, fill = "pink") +
  xlab("Bias")+
  ylab("Estimate Densitites")+
  theme_bw()+
  geom_vline(xintercept = median(db$bias), linetype = "dashed", size = 1.5) +
  ggtitle("Simulated Skier 9")

# bias plot
b10w <- ggplot(draws_df_weighted) +
  geom_density(aes(`bias_posterior[10]`), alpha = 0.6, fill = "lightblue") +
  geom_density(aes(`bias_prior[10]`), alpha = 0.6, fill = "pink") +
  xlab("Bias")+
  ylab("Estimate Densitites")+
  theme_bw()+
  geom_vline(xintercept = median(db$bias), linetype = "dashed", size = 1.5) +
  ggtitle("Simulated Skier 10")

pbw_all <- b1w+b2w+b3w+b4w+b5w+b6w+b7w+b8w+b9w+b10w+plot_annotation(title = "Prior Posterior Update Checks for the Simulated Skiers", subtitle = "β Parameter",
                                                         theme = theme(plot.title = element_text(size = 20, hjust = 0.5),plot.subtitle = element_text(size=15, hjust = 0.5)))

pbw_all
```

This chunk has all the prior posterior update plots for weight 1
```{r}
### prior posterior update plots for w1  ###
# w1 plots
w1w1 <- ggplot(draws_df_weighted) +
  geom_density(aes(`w1_posterior[1]`), alpha = 0.6, fill = "lightblue") +
  geom_density(aes(`w1_prior[1]`), alpha = 0.6, fill = "pink") +
  xlab("ω1")+
  ylab("Estimate Densitites")+
  theme_bw()+
  geom_vline(xintercept = median(db$w1), linetype = "dashed", size = 1.5) +
  ggtitle("Simulated Skier 1")

w2w1 <- ggplot(draws_df_weighted) +
  geom_density(aes(`w1_posterior[2]`), alpha = 0.6, fill = "lightblue") +
  geom_density(aes(`w1_prior[2]`), alpha = 0.6, fill = "pink") +
  xlab("ω1")+
  ylab("Estimate Densitites")+
  theme_bw()+
  geom_vline(xintercept = median(db$w1), linetype = "dashed", size = 1.5) +
  ggtitle("Simulated Skier 2")

w3w1 <- ggplot(draws_df_weighted) +
  geom_density(aes(`w1_posterior[3]`), alpha = 0.6, fill = "lightblue") +
  geom_density(aes(`w1_prior[3]`), alpha = 0.6, fill = "pink") +
  xlab("ω1")+
  ylab("Estimate Densitites")+
  theme_bw()+
  geom_vline(xintercept = median(db$w1), linetype = "dashed", size = 1.5) +
  ggtitle("Simulated Skier 3")

w4w1 <- ggplot(draws_df_weighted) +
  geom_density(aes(`w1_posterior[4]`), alpha = 0.6, fill = "lightblue") +
  geom_density(aes(`w1_prior[4]`), alpha = 0.6, fill = "pink") +
  xlab("ω1")+
  ylab("Estimate Densitites")+
  theme_bw()+
  geom_vline(xintercept = median(db$w1), linetype = "dashed", size = 1.5) +
  ggtitle("Simulated Skier 4")

w5w1 <- ggplot(draws_df_weighted) +
  geom_density(aes(`w1_posterior[5]`), alpha = 0.6, fill = "lightblue") +
  geom_density(aes(`w1_prior[5]`), alpha = 0.6, fill = "pink") +
  xlab("ω1")+
  ylab("Estimate Densitites")+
  theme_bw()+
  geom_vline(xintercept = median(db$w1), linetype = "dashed", size = 1.5) +
  ggtitle("Simulated Skier 5")

w6w1 <- ggplot(draws_df_weighted) +
  geom_density(aes(`w1_posterior[6]`), alpha = 0.6, fill = "lightblue") +
  geom_density(aes(`w1_prior[6]`), alpha = 0.6, fill = "pink") +
  xlab("ω1")+
  ylab("Estimate Densitites")+
  theme_bw()+
  geom_vline(xintercept = median(db$w1), linetype = "dashed", size = 1.5) +
  ggtitle("Simulated Skier 6")

w7w1 <- ggplot(draws_df_weighted) +
  geom_density(aes(`w1_posterior[7]`), alpha = 0.6, fill = "lightblue") +
  geom_density(aes(`w1_prior[7]`), alpha = 0.6, fill = "pink") +
  xlab("ω1")+
  ylab("Estimate Densitites")+
  theme_bw()+
  geom_vline(xintercept = median(db$w1), linetype = "dashed", size = 1.5) +
  ggtitle("Simulated Skier 7")

w8w1 <- ggplot(draws_df_weighted) +
  geom_density(aes(`w1_posterior[8]`), alpha = 0.6, fill = "lightblue") +
  geom_density(aes(`w1_prior[8]`), alpha = 0.6, fill = "pink") +
  xlab("ω1")+
  ylab("Estimate Densitites")+
  theme_bw()+
  geom_vline(xintercept = median(db$w1), linetype = "dashed", size = 1.5) +
  ggtitle("Simulated Skier 8")

w9w1 <- ggplot(draws_df_weighted) +
  geom_density(aes(`w1_posterior[9]`), alpha = 0.6, fill = "lightblue") +
  geom_density(aes(`w1_prior[9]`), alpha = 0.6, fill = "pink") +
  xlab("ω1")+
  ylab("Estimate Densitites")+
  theme_bw()+
  geom_vline(xintercept = median(db$w1), linetype = "dashed", size = 1.5) +
  ggtitle("Simulated Skier 9")

w10w1 <- ggplot(draws_df_weighted) +
  geom_density(aes(`w1_posterior[10]`), alpha = 0.6, fill = "lightblue") +
  geom_density(aes(`w1_prior[10]`), alpha = 0.6, fill = "pink") +
  xlab("ω1")+
  ylab("Estimate Densitites")+
  theme_bw()+
  geom_vline(xintercept = median(db$w1), linetype = "dashed", size = 1.5) +
  ggtitle("Simulated Skier 10")

pbw1_all <- w1w1+w2w1+w3w1+w4w1+w5w1+w6w1+w7w1+w8w1+w9w1+w10w1+plot_annotation(title = "Prior Posterior Update Checks for the Simulated Skiers", subtitle = "ω1 Parameter",
                                                         theme = theme(plot.title = element_text(size = 20, hjust = 0.5),plot.subtitle = element_text(size=15, hjust = 0.5)))

pbw1_all

```

This chunk has all the prior posterior update plots for weight 2
```{r}
### prior posterior update plots for w2  ###
# w1 plots
w1w2 <- ggplot(draws_df_weighted) +
  geom_density(aes(`w2_posterior[1]`), alpha = 0.6, fill = "lightblue") +
  geom_density(aes(`w2_prior[1]`), alpha = 0.6, fill = "pink") +
  xlab("ω2")+
  ylab("Estimate Densitites")+
  theme_bw()+
  geom_vline(xintercept = median(db$w2), linetype = "dashed", size = 1.5) +
  ggtitle("Simulated Skier 1")

w2w2 <- ggplot(draws_df_weighted) +
  geom_density(aes(`w2_posterior[2]`), alpha = 0.6, fill = "lightblue") +
  geom_density(aes(`w2_prior[2]`), alpha = 0.6, fill = "pink") +
  xlab("ω2")+
  ylab("Estimate Densitites")+
  theme_bw()+
  geom_vline(xintercept = median(db$w2), linetype = "dashed", size = 1.5) +
  ggtitle("Simulated Skier 2")

w3w2 <- ggplot(draws_df_weighted) +
  geom_density(aes(`w2_posterior[3]`), alpha = 0.6, fill = "lightblue") +
  geom_density(aes(`w2_prior[3]`), alpha = 0.6, fill = "pink") +
  xlab("ω2")+
  ylab("Estimate Densitites")+
  theme_bw()+
  geom_vline(xintercept = median(db$w2), linetype = "dashed", size = 1.5) +
  ggtitle("Simulated Skier 3")

w4w2 <- ggplot(draws_df_weighted) +
  geom_density(aes(`w2_posterior[4]`), alpha = 0.6, fill = "lightblue") +
  geom_density(aes(`w2_prior[4]`), alpha = 0.6, fill = "pink") +
  xlab("ω2")+
  ylab("Estimate Densitites")+
  theme_bw()+
  geom_vline(xintercept = median(db$w2), linetype = "dashed", size = 1.5) +
  ggtitle("Simulated Skier 4")

w5w2 <- ggplot(draws_df_weighted) +
  geom_density(aes(`w2_posterior[5]`), alpha = 0.6, fill = "lightblue") +
  geom_density(aes(`w2_prior[5]`), alpha = 0.6, fill = "pink") +
  xlab("ω2")+
  ylab("Estimate Densitites")+
  theme_bw()+
  geom_vline(xintercept = median(db$w2), linetype = "dashed", size = 1.5) +
  ggtitle("Simulated Skier 5")

w6w2 <- ggplot(draws_df_weighted) +
  geom_density(aes(`w2_posterior[6]`), alpha = 0.6, fill = "lightblue") +
  geom_density(aes(`w2_prior[6]`), alpha = 0.6, fill = "pink") +
  xlab("ω2")+
  ylab("Estimate Densitites")+
  theme_bw()+
  geom_vline(xintercept = median(db$w2), linetype = "dashed", size = 1.5) +
  ggtitle("Simulated Skier 6")

w7w2 <- ggplot(draws_df_weighted) +
  geom_density(aes(`w2_posterior[7]`), alpha = 0.6, fill = "lightblue") +
  geom_density(aes(`w2_prior[7]`), alpha = 0.6, fill = "pink") +
  xlab("ω2")+
  ylab("Estimate Densitites")+
  theme_bw()+
  geom_vline(xintercept = median(db$w2), linetype = "dashed", size = 1.5) +
  ggtitle("Simulated Skier 7")

w8w2 <- ggplot(draws_df_weighted) +
  geom_density(aes(`w2_posterior[8]`), alpha = 0.6, fill = "lightblue") +
  geom_density(aes(`w2_prior[8]`), alpha = 0.6, fill = "pink") +
  xlab("ω2")+
  ylab("Estimate Densitites")+
  theme_bw()+
  geom_vline(xintercept = median(db$w2), linetype = "dashed", size = 1.5) +
  ggtitle("Simulated Skier 8")

w9w2 <- ggplot(draws_df_weighted) +
  geom_density(aes(`w2_posterior[9]`), alpha = 0.6, fill = "lightblue") +
  geom_density(aes(`w2_prior[9]`), alpha = 0.6, fill = "pink") +
  xlab("ω2")+
  ylab("Estimate Densitites")+
  theme_bw()+
  geom_vline(xintercept = median(db$w2), linetype = "dashed", size = 1.5) +
  ggtitle("Simulated Skier 9")

w10w2 <- ggplot(draws_df_weighted) +
  geom_density(aes(`w2_posterior[10]`), alpha = 0.6, fill = "lightblue") +
  geom_density(aes(`w2_prior[10]`), alpha = 0.6, fill = "pink") +
  xlab("ω2")+
  ylab("Estimate Densitites")+
  theme_bw()+
  geom_vline(xintercept = median(db$w2), linetype = "dashed", size = 1.5) +
  ggtitle("Simulated Skier 10")

pbw2_all <- w1w2+w2w2+w3w2+w4w2+w5w2+w6w2+w7w2+w8w2+w9w2+w10w2+plot_annotation(title = "Prior Posterior Update Checks for the Simulated Skiers", subtitle = "ω2 Parameter",
                                                         theme = theme(plot.title = element_text(size = 20, hjust = 0.5),plot.subtitle = element_text(size=15, hjust = 0.5)))

pbw2_all
```

This chunk has all the chains mixing traceplots for bias
```{r}
# chains mixing plots bias
mp1 <- ggplot(draws_df_weighted, aes(.iteration, `bias[1]`, group = .chain, color = .chain)) +
  geom_line(alpha = 0.5) +
  theme_classic()
mp2 <- ggplot(draws_df_weighted, aes(.iteration, `bias[2]`, group = .chain, color = .chain)) +
  geom_line(alpha = 0.5) +
  theme_classic()
mp3 <- ggplot(draws_df_weighted, aes(.iteration, `bias[3]`, group = .chain, color = .chain)) +
  geom_line(alpha = 0.5) +
  theme_classic()
mp4 <- ggplot(draws_df_weighted, aes(.iteration, `bias[4]`, group = .chain, color = .chain)) +
  geom_line(alpha = 0.5) +
  theme_classic()
mp5 <- ggplot(draws_df_weighted, aes(.iteration, `bias[5]`, group = .chain, color = .chain)) +
  geom_line(alpha = 0.5) +
  theme_classic()
mp6 <- ggplot(draws_df_weighted, aes(.iteration, `bias[6]`, group = .chain, color = .chain)) +
  geom_line(alpha = 0.5) +
  theme_classic()
mp7 <- ggplot(draws_df_weighted, aes(.iteration, `bias[7]`, group = .chain, color = .chain)) +
  geom_line(alpha = 0.5) +
  theme_classic()
mp8 <- ggplot(draws_df_weighted, aes(.iteration, `bias[8]`, group = .chain, color = .chain)) +
  geom_line(alpha = 0.5) +
  theme_classic()
mp9 <- ggplot(draws_df_weighted, aes(.iteration, `bias[9]`, group = .chain, color = .chain)) +
  geom_line(alpha = 0.5) +
  theme_classic()
mp10 <- ggplot(draws_df_weighted, aes(.iteration, `bias[10]`, group = .chain, color = .chain)) +
  geom_line(alpha = 0.5) +
  theme_classic()

mix_w_all <- ggarrange(mp1, mp2, mp3, mp4, mp5, mp6, mp7, mp8, mp9, mp10)

annotate_figure(mix_w_all, top = text_grob("Chains Mixing Plot Weighted Bayes Model for the β Parameter", 
                face = "bold", size = 14))

mix_w_all
```

This chunk has all the chains mixing traceplots for w1
```{r}
# chains mixing plots w1
mpw1 <- ggplot(draws_df_weighted, aes(.iteration, `w1[1]`, group = .chain, color = .chain)) +
  geom_line(alpha = 0.5) +
  theme_classic()

mpw2 <- ggplot(draws_df_weighted, aes(.iteration, `w1[2]`, group = .chain, color = .chain)) +
  geom_line(alpha = 0.5) +
  theme_classic()

mpw3 <- ggplot(draws_df_weighted, aes(.iteration, `w1[3]`, group = .chain, color = .chain)) +
  geom_line(alpha = 0.5) +
  theme_classic()

mpw4 <- ggplot(draws_df_weighted, aes(.iteration, `w1[4]`, group = .chain, color = .chain)) +
  geom_line(alpha = 0.5) +
  theme_classic()

mpw5 <- ggplot(draws_df_weighted, aes(.iteration, `w1[5]`, group = .chain, color = .chain)) +
  geom_line(alpha = 0.5) +
  theme_classic()

mpw6 <- ggplot(draws_df_weighted, aes(.iteration, `w1[6]`, group = .chain, color = .chain)) +
  geom_line(alpha = 0.5) +
  theme_classic()

mpw7 <- ggplot(draws_df_weighted, aes(.iteration, `w1[7]`, group = .chain, color = .chain)) +
  geom_line(alpha = 0.5) +
  theme_classic()

mpw8 <- ggplot(draws_df_weighted, aes(.iteration, `w1[8]`, group = .chain, color = .chain)) +
  geom_line(alpha = 0.5) +
  theme_classic()

mpw9 <- ggplot(draws_df_weighted, aes(.iteration, `w1[9]`, group = .chain, color = .chain)) +
  geom_line(alpha = 0.5) +
  theme_classic()

mpw10 <- ggplot(draws_df_weighted, aes(.iteration, `w1[10]`, group = .chain, color = .chain)) +
  geom_line(alpha = 0.5) +
  theme_classic()

mix_w1_all <- ggarrange(mpw1, mpw2, mpw3, mpw4, mpw5, mpw6, mpw7, mpw8, mpw9, mpw10)

annotate_figure(mix_w1_all, top = text_grob("Chains Mixing Plot Weighted Bayes Model for the ω1 Parameter", 
                face = "bold", size = 14))

mix_w1_all
```

This chunk has all the chains mixing traceplots for w2
```{r}
# chains mixing plot w2
mp2w1 <- ggplot(draws_df_weighted, aes(.iteration, `w2[1]`, group = .chain, color = .chain)) +
  geom_line(alpha = 0.5) +
  theme_classic()

mp2w2 <- ggplot(draws_df_weighted, aes(.iteration, `w2[2]`, group = .chain, color = .chain)) +
  geom_line(alpha = 0.5) +
  theme_classic()

mp2w3 <- ggplot(draws_df_weighted, aes(.iteration, `w2[3]`, group = .chain, color = .chain)) +
  geom_line(alpha = 0.5) +
  theme_classic()

mp2w4 <- ggplot(draws_df_weighted, aes(.iteration, `w2[4]`, group = .chain, color = .chain)) +
  geom_line(alpha = 0.5) +
  theme_classic()

mp2w5 <- ggplot(draws_df_weighted, aes(.iteration, `w2[5]`, group = .chain, color = .chain)) +
  geom_line(alpha = 0.5) +
  theme_classic()

mp2w6 <- ggplot(draws_df_weighted, aes(.iteration, `w2[6]`, group = .chain, color = .chain)) +
  geom_line(alpha = 0.5) +
  theme_classic()

mp2w7 <- ggplot(draws_df_weighted, aes(.iteration, `w2[7]`, group = .chain, color = .chain)) +
  geom_line(alpha = 0.5) +
  theme_classic()

mp2w8 <- ggplot(draws_df_weighted, aes(.iteration, `w2[8]`, group = .chain, color = .chain)) +
  geom_line(alpha = 0.5) +
  theme_classic()

mp2w9 <- ggplot(draws_df_weighted, aes(.iteration, `w2[9]`, group = .chain, color = .chain)) +
  geom_line(alpha = 0.5) +
  theme_classic()

mp2w10 <- ggplot(draws_df_weighted, aes(.iteration, `w2[10]`, group = .chain, color = .chain)) +
  geom_line(alpha = 0.5) +
  theme_classic()

mix_w2_all <- ggarrange(mp2w1, mp2w2, mp2w3, mp2w4, mp2w5, mp2w6, mp2w7, mp2w8, mp2w9, mp2w10)

annotate_figure(mix_w1_all, top = text_grob("Chains Mixing Plot Weighted Bayes Model for the ω2 Parameter", 
                face = "bold", size = 14))

mix_w2_all
```

This chunk creates different levels of means and standard deviations for a prior sensitivity analysis
```{r}
# adding different priors for bias
prior_mean <- seq(-3, 3, .5)
prior_sd <- seq(0.1, 1, 0.1)
priors <-  expand.grid(prior_mean, prior_sd)
priors <- tibble(prior_mean = priors$Var1, prior_sd = priors$Var2)

# feed R the stan model with priors
file <- file.path("wbPriors.stan")
mod <- cmdstan_model(file, 
                     cpp_options = list(stan_threads = TRUE),
                     stanc_options = list("O1"))

# use all cores on the computer
plan(multisession, workers = 4)

# calling function self-written function that simulates data and fits it by sequences of different priors
prior_sens_dfW <- future_pmap_dfr(priors, sim_d_and_fit_weighted, .options = furrr_options(seed = TRUE))
```

```{r}
### prior sensitivity plots ###
#  bias
ggplot(prior_sens_dfW, aes(prior_mean, bias_posterior1)) +
  xlab("Prior Mean")+
  ylab("Bias Posterior")+
  geom_point(alpha = 0.1) +
  geom_hline(yintercept = 0.8, color = "red") +
  geom_smooth() +
  facet_wrap(.~prior_sd, labeller = labeller(prior_sd = 
    c("0.1" = "prior standard deviation: 0.1",
      "0.2" = "prior standard deviation: 0.2",
      "0.3" = "prior standard deviation: 0.3",
      "0.4" = "prior standard deviation: 0.4",
      "0.5" = "prior standard deviation: 0.5",
      "0.6" = "prior standard deviation: 0.6",
      "0.7" = "prior standard deviation: 0.7",
      "0.8" = "prior standard deviation: 0.8",
      "0.9" = "prior standard deviation: 0.9",
      "1" = "prior standard deviation: 1"
      )))+
  theme_classic()

# weight 1
ggplot(prior_sens_dfW, aes(prior_mean, w1_posterior1)) +
  xlab("Prior Mean")+
  ylab("ω1 Posterior")+
  geom_point(alpha = 0.1) +
  geom_hline(yintercept = 0.8, color = "red") +
  geom_smooth() +
  facet_wrap(.~prior_sd, labeller = labeller(prior_sd = 
    c("0.1" = "prior standard deviation: 0.1",
      "0.2" = "prior standard deviation: 0.2",
      "0.3" = "prior standard deviation: 0.3",
      "0.4" = "prior standard deviation: 0.4",
      "0.5" = "prior standard deviation: 0.5",
      "0.6" = "prior standard deviation: 0.6",
      "0.7" = "prior standard deviation: 0.7",
      "0.8" = "prior standard deviation: 0.8",
      "0.9" = "prior standard deviation: 0.9",
      "1" = "prior standard deviation: 1"
      )))+
  theme_classic()

# weight 2
ggplot(prior_sens_dfW, aes(prior_mean, w2_posterior1)) +
  xlab("Prior Mean")+
  ylab("ω2 Posterior")+
  geom_point(alpha = 0.1) +
  geom_hline(yintercept = 0.8, color = "red") +
  geom_smooth() +
  facet_wrap(.~prior_sd, labeller = labeller(prior_sd = 
    c("0.1" = "prior standard deviation: 0.1",
      "0.2" = "prior standard deviation: 0.2",
      "0.3" = "prior standard deviation: 0.3",
      "0.4" = "prior standard deviation: 0.4",
      "0.5" = "prior standard deviation: 0.5",
      "0.6" = "prior standard deviation: 0.6",
      "0.7" = "prior standard deviation: 0.7",
      "0.8" = "prior standard deviation: 0.8",
      "0.9" = "prior standard deviation: 0.9",
      "1" = "prior standard deviation: 1"
      )))+
  theme_classic()
```


```{r}
# weight plots

b2w1 <- ggplot(draws_df_weighted) +
  geom_density(aes(`w1_posterior[1]`), alpha = 0.6, fill = "lightblue") +
  geom_density(aes(`w1_prior[1]`), alpha = 0.6, fill = "pink") +
  xlab("ω1")+
  ylab("Estimate Densitites")+
  theme_bw()+
  geom_vline(xintercept = median(db$w1), linetype = "dashed", size = 1.5) +
  ggtitle("Simulated Skier 1")

b2w2 <- ggplot(draws_df_weighted) +
  geom_density(aes(`w2_posterior[1]`), alpha = 0.6, fill = "lightblue") +
  geom_density(aes(`w2_prior[1]`), alpha = 0.6, fill = "pink") +
  xlab("ω1")+
  ylab("Estimate Densitites")+
  theme_bw()+
  geom_vline(xintercept = median(db$w2), linetype = "dashed", size = 1.5) +
  ggtitle("Simulated Skier 1")

b1w
b2w1
b2w2
```


```{r}
# leave one out cross-validation information criteria
samples_weighted$loo()
```



```{r}
# chains mixing plot
p1b <- ggplot(draws_df_weighted, aes(.iteration, `bias[1]`, group = .chain, color = .chain)) +
  geom_line(alpha = 0.5) +
  theme_classic()

p1w1 <- ggplot(draws_df_weighted, aes(.iteration, w1, group = .chain, color = .chain)) +
  geom_line(alpha = 0.5) +
  theme_classic()

# bias plot
b1 <- ggplot(draws_df_weighted) +
  geom_density(aes(`bias_posterior[1]`), alpha = 0.6, fill = "lightblue") +
    annotate("text", colour = "lightblue", x = 0.01, y = 46, label = "Posterior Distribution Bias" , hjust = 0)+
  geom_density(aes(`bias_prior[1]`), alpha = 0.6, fill = "pink") +
    annotate("text", colour = "pink", x = 0.01, y = 43, label = "Prior Distribution Bias", hjust =0)+
  xlab("Bias")+
  ylab("Estimate Densitites")+
  theme_bw()+
  geom_vline(xintercept = mean(db$bias), linetype = "dashed", size = 1.5) +
    annotate("text", x = 0.01, y = 40,  label="True Bias", hjust = 0)+
  geom_rect(aes(xmin = 0, xmax = 0.61, ymin = 38, ymax = 48), 
            fill = "white", color = "black", alpha = 0)+
  ggtitle("Simulated Skier 1")


# bias plot
w1 <- ggplot(draws_df_weighted) +
  geom_density(aes(`w1[1]`), alpha = 0.6, fill = "lightblue") +
    annotate("text", colour = "lightblue", x = 0.01, y = 46, label = "Posterior Distribution Bias" , hjust = 0)+
  geom_density(aes(`w1_prior[1]`), alpha = 0.6, fill = "pink") +
    annotate("text", colour = "pink", x = 0.01, y = 43, label = "Prior Distribution Bias", hjust =0)+
  xlab("Bias")+
  ylab("Estimate Densitites")+
  theme_bw()+
  geom_vline(xintercept = mean(db$bias), linetype = "dashed", size = 1.5) +
    annotate("text", x = 0.01, y = 40,  label="True Bias", hjust = 0)+
  geom_rect(aes(xmin = 0, xmax = 0.61, ymin = 38, ymax = 48), 
            fill = "white", color = "black", alpha = 0)+
  ggtitle("Simulated Skier 1")

# bias plot
w2 <- ggplot(draws_df_weighted) +
  geom_density(aes(`w2[1]`), alpha = 0.6, fill = "lightblue") +
    annotate("text", colour = "lightblue", x = 0.01, y = 46, label = "Posterior Distribution Bias" , hjust = 0)+
  geom_density(aes(`w2_prior[1]`), alpha = 0.6, fill = "pink") +
    annotate("text", colour = "pink", x = 0.01, y = 43, label = "Prior Distribution Bias", hjust =0)+
  xlab("Bias")+
  ylab("Estimate Densitites")+
  theme_bw()+
  geom_vline(xintercept = mean(db$bias), linetype = "dashed", size = 1.5) +
    annotate("text", x = 0.01, y = 40,  label="True Bias", hjust = 0)+
  geom_rect(aes(xmin = 0, xmax = 0.61, ymin = 38, ymax = 48), 
            fill = "white", color = "black", alpha = 0)+
  ggtitle("Simulated Skier 1")

w1+w2
```

```{r}
# do the parameters influence each other?
ggplot(draws_df_weighted) +
  geom_point(aes(`bias[2]`, `w2[2]`), alpha = 0.3) +
  theme_bw()

ggplot(draws_df_weighted) +
  geom_point(aes(`bias[2]`, `w1[2]`), alpha = 0.3) +
  theme_bw()

ggplot(draws_df_weighted) +
  geom_point(aes(`w1[2]`, `w2[2]`), alpha = 0.3) +
  theme_bw()
```


```{r}
### more plots ###
# bias plot
w11 <- ggplot(draws_df_weighted) +
  geom_density(aes(`w1[1]`), alpha = 0.6, fill = "lightblue") +
    annotate("text", colour = "lightblue", x = 0.01, y = 46, label = "Posterior Distribution Bias" , hjust = 0)+
  geom_density(aes(`w1_prior[1]`), alpha = 0.6, fill = "pink") +
    annotate("text", colour = "pink", x = 0.01, y = 43, label = "Prior Distribution Bias", hjust =0)+
  xlab("Bias")+
  ylab("Estimate Densitites")+
  theme_bw()+
  geom_vline(xintercept = mean(db$bias), linetype = "dashed", size = 1.5) +
    annotate("text", x = 0.01, y = 40,  label="True Bias", hjust = 0)+
  geom_rect(aes(xmin = 0, xmax = 0.61, ymin = 38, ymax = 48), 
            fill = "white", color = "black", alpha = 0)+
  ggtitle("Simulated Skier 1")

# bias plot
w12 <- ggplot(draws_df_weighted) +
  geom_density(aes(`w1[2]`), alpha = 0.6, fill = "lightblue") +
    annotate("text", colour = "lightblue", x = 0.01, y = 46, label = "Posterior Distribution Bias" , hjust = 0)+
  geom_density(aes(`w1_prior[2]`), alpha = 0.6, fill = "pink") +
    annotate("text", colour = "pink", x = 0.01, y = 43, label = "Prior Distribution Bias", hjust =0)+
  xlab("Bias")+
  ylab("Estimate Densitites")+
  theme_bw()+
  geom_vline(xintercept = mean(db$bias), linetype = "dashed", size = 1.5) +
    annotate("text", x = 0.01, y = 40,  label="True Bias", hjust = 0)+
  geom_rect(aes(xmin = 0, xmax = 0.61, ymin = 38, ymax = 48), 
            fill = "white", color = "black", alpha = 0)+
  ggtitle("Simulated Skier 1")

# bias plot
w13 <- ggplot(draws_df_weighted) +
  geom_density(aes(`w1[3]`), alpha = 0.6, fill = "lightblue") +
    annotate("text", colour = "lightblue", x = 0.01, y = 46, label = "Posterior Distribution Bias" , hjust = 0)+
  geom_density(aes(`w1_prior[3]`), alpha = 0.6, fill = "pink") +
    annotate("text", colour = "pink", x = 0.01, y = 43, label = "Prior Distribution Bias", hjust =0)+
  xlab("Bias")+
  ylab("Estimate Densitites")+
  theme_bw()+
  geom_vline(xintercept = mean(db$bias), linetype = "dashed", size = 1.5) +
    annotate("text", x = 0.01, y = 40,  label="True Bias", hjust = 0)+
  geom_rect(aes(xmin = 0, xmax = 0.61, ymin = 38, ymax = 48), 
            fill = "white", color = "black", alpha = 0)+
  ggtitle("Simulated Skier 1")

# bias plot
w14 <- ggplot(draws_df_weighted) +
  geom_density(aes(`w1[4]`), alpha = 0.6, fill = "lightblue") +
    annotate("text", colour = "lightblue", x = 0.01, y = 46, label = "Posterior Distribution Bias" , hjust = 0)+
  geom_density(aes(`w1_prior[4]`), alpha = 0.6, fill = "pink") +
    annotate("text", colour = "pink", x = 0.01, y = 43, label = "Prior Distribution Bias", hjust =0)+
  xlab("Bias")+
  ylab("Estimate Densitites")+
  theme_bw()+
  geom_vline(xintercept = mean(db$bias), linetype = "dashed", size = 1.5) +
    annotate("text", x = 0.01, y = 40,  label="True Bias", hjust = 0)+
  geom_rect(aes(xmin = 0, xmax = 0.61, ymin = 38, ymax = 48), 
            fill = "white", color = "black", alpha = 0)+
  ggtitle("Simulated Skier 1")

# bias plot
w15 <- ggplot(draws_df_weighted) +
  geom_density(aes(`w1[5]`), alpha = 0.6, fill = "lightblue") +
    annotate("text", colour = "lightblue", x = 0.01, y = 46, label = "Posterior Distribution Bias" , hjust = 0)+
  geom_density(aes(`w1_prior[5]`), alpha = 0.6, fill = "pink") +
    annotate("text", colour = "pink", x = 0.01, y = 43, label = "Prior Distribution Bias", hjust =0)+
  xlab("Bias")+
  ylab("Estimate Densitites")+
  theme_bw()+
  geom_vline(xintercept = mean(db$bias), linetype = "dashed", size = 1.5) +
    annotate("text", x = 0.01, y = 40,  label="True Bias", hjust = 0)+
  geom_rect(aes(xmin = 0, xmax = 0.61, ymin = 38, ymax = 48), 
            fill = "white", color = "black", alpha = 0)+
  ggtitle("Simulated Skier 1")

# bias plot
w16 <- ggplot(draws_df_weighted) +
  geom_density(aes(`w1[6]`), alpha = 0.6, fill = "lightblue") +
    annotate("text", colour = "lightblue", x = 0.01, y = 46, label = "Posterior Distribution Bias" , hjust = 0)+
  geom_density(aes(`w1_prior[6]`), alpha = 0.6, fill = "pink") +
    annotate("text", colour = "pink", x = 0.01, y = 43, label = "Prior Distribution Bias", hjust =0)+
  xlab("Bias")+
  ylab("Estimate Densitites")+
  theme_bw()+
  geom_vline(xintercept = mean(db$bias), linetype = "dashed", size = 1.5) +
    annotate("text", x = 0.01, y = 40,  label="True Bias", hjust = 0)+
  geom_rect(aes(xmin = 0, xmax = 0.61, ymin = 38, ymax = 48), 
            fill = "white", color = "black", alpha = 0)+
  ggtitle("Simulated Skier 1")

# bias plot
w17 <- ggplot(draws_df_weighted) +
  geom_density(aes(`w1[7]`), alpha = 0.6, fill = "lightblue") +
    annotate("text", colour = "lightblue", x = 0.01, y = 46, label = "Posterior Distribution Bias" , hjust = 0)+
  geom_density(aes(`w1_prior[7]`), alpha = 0.6, fill = "pink") +
    annotate("text", colour = "pink", x = 0.01, y = 43, label = "Prior Distribution Bias", hjust =0)+
  xlab("Bias")+
  ylab("Estimate Densitites")+
  theme_bw()+
  geom_vline(xintercept = mean(db$bias), linetype = "dashed", size = 1.5) +
    annotate("text", x = 0.01, y = 40,  label="True Bias", hjust = 0)+
  geom_rect(aes(xmin = 0, xmax = 0.61, ymin = 38, ymax = 48), 
            fill = "white", color = "black", alpha = 0)+
  ggtitle("Simulated Skier 1")

# bias plot
w18 <- ggplot(draws_df_weighted) +
  geom_density(aes(`w1[8]`), alpha = 0.6, fill = "lightblue") +
    annotate("text", colour = "lightblue", x = 0.01, y = 46, label = "Posterior Distribution Bias" , hjust = 0)+
  geom_density(aes(`w1_prior[8]`), alpha = 0.6, fill = "pink") +
    annotate("text", colour = "pink", x = 0.01, y = 43, label = "Prior Distribution Bias", hjust =0)+
  xlab("Bias")+
  ylab("Estimate Densitites")+
  theme_bw()+
  geom_vline(xintercept = mean(db$bias), linetype = "dashed", size = 1.5) +
    annotate("text", x = 0.01, y = 40,  label="True Bias", hjust = 0)+
  geom_rect(aes(xmin = 0, xmax = 0.61, ymin = 38, ymax = 48), 
            fill = "white", color = "black", alpha = 0)+
  ggtitle("Simulated Skier 1")

# bias plot
w19 <- ggplot(draws_df_weighted) +
  geom_density(aes(`w1[9]`), alpha = 0.6, fill = "lightblue") +
    annotate("text", colour = "lightblue", x = 0.01, y = 46, label = "Posterior Distribution Bias" , hjust = 0)+
  geom_density(aes(`w1_prior[9]`), alpha = 0.6, fill = "pink") +
    annotate("text", colour = "pink", x = 0.01, y = 43, label = "Prior Distribution Bias", hjust =0)+
  xlab("Bias")+
  ylab("Estimate Densitites")+
  theme_bw()+
  geom_vline(xintercept = mean(db$bias), linetype = "dashed", size = 1.5) +
    annotate("text", x = 0.01, y = 40,  label="True Bias", hjust = 0)+
  geom_rect(aes(xmin = 0, xmax = 0.61, ymin = 38, ymax = 48), 
            fill = "white", color = "black", alpha = 0)+
  ggtitle("Simulated Skier 1")

# bias plot
w110 <- ggplot(draws_df_weighted) +
  geom_density(aes(`w1[10]`), alpha = 0.6, fill = "lightblue") +
    annotate("text", colour = "lightblue", x = 0.01, y = 46, label = "Posterior Distribution Bias" , hjust = 0)+
  geom_density(aes(`w1_prior[10]`), alpha = 0.6, fill = "pink") +
    annotate("text", colour = "pink", x = 0.01, y = 43, label = "Prior Distribution Bias", hjust =0)+
  xlab("Bias")+
  ylab("Estimate Densitites")+
  theme_bw()+
  geom_vline(xintercept = mean(db$bias), linetype = "dashed", size = 1.5) +
    annotate("text", x = 0.01, y = 40,  label="True Bias", hjust = 0)+
  geom_rect(aes(xmin = 0, xmax = 0.61, ymin = 38, ymax = 48), 
            fill = "white", color = "black", alpha = 0)+
  ggtitle("Simulated Skier 1")

w11+w12+w13+w14+w15+w16+w17+w18+w19+w110
```

```{r}
# parameter recovery for bias
parameter_recovery_dfbw <- NULL  

for (biasLvl in unique(db$bias)){
 
  dataWeightedBayesParam <- db %>% subset(
      bias == biasLvl  
    )
  
  # Create the data
samples_w <- mod_WeightedBayes$sample( 
  data = list(
  N = nrow(dataWeightedBayesParam),
  S = 1,
  outcome = as.matrix(dataWeightedBayesParam$outcome),
  Source1 = as.matrix(dataWeightedBayesParam$Source1),
  Source2 = as.matrix(dataWeightedBayesParam$Source2)
),

  seed = 123,
  chains = 2,
  parallel_chains = 2,
  threads_per_chain = 2,
  iter_warmup = 1500,
  iter_sampling = 3000,
  refresh = 0,
  max_treedepth = 10,
  adapt_delta = 0.99
      )
   
  draws_df_param_recov_b <- as_draws_df(samples_w$draws()) 
  temp_paramb <- tibble(
                   biasEstScaled = inv_logit_scaled(draws_df_param_recov_b$`bias[1]`), 
                   biasTrue = biasLvl,
                   biasEst = draws_df_param_recov_b$`bias[1]`

                   )
    
    
    if (exists("parameter_recovery_dfbw")) {parameter_recovery_dfbw <- rbind(parameter_recovery_dfbw, temp_paramb)} else {parameter_recovery_dfbw <- temp_paramb}
    
  }
```

```{r}
# parameter recovery for weight 1

parameter_recovery_dfw1 <- NULL  

for (weightLvl1 in unique(db$w1)) {
 
  dataWeightedBayesParam <- db %>% subset(
      w1 == weightLvl1
    )
  
  # Create the data
samples_w <- mod_WeightedBayes$sample( 
  data = list(
  N = nrow(dataWeightedBayesParam),
  S = 1,
  outcome = as.matrix(dataWeightedBayesParam$outcome),
  Source1 = as.matrix(dataWeightedBayesParam$Source1),
  Source2 = as.matrix(dataWeightedBayesParam$Source2)
),

  seed = 123,
  chains = 2,
  parallel_chains = 2,
  threads_per_chain = 2,
  iter_warmup = 1500,
  iter_sampling = 3000,
  refresh = 0,
  max_treedepth = 10,
  adapt_delta = 0.99
      )
   
  draws_df_param_recov_w1 <- as_draws_df(samples_w$draws()) 
  temp_paramw1 <- tibble(
                   w1EstScaled = inv_logit_scaled(draws_df_param_recov_w1$`w1[1]`), 
                   w1True = weightLvl1, 
                   w1Est = draws_df_param_recov_w1$`w1[1]`
                   )
    
    
    if (exists("parameter_recovery_dfw1")) {parameter_recovery_dfw1 <- rbind(parameter_recovery_dfw1, temp_paramw1)} else {parameter_recovery_dfw1 <- temp_paramw1}
    
  }

```

```{r}
# parameter recovery for weight 2
parameter_recovery_dfw2 <- NULL  

  for (weightLvl2 in unique(db$w2)){
 
  
  dataWeightedBayesParam <- db %>% subset(
      w2 == weightLvl2 
    )
  
  # Create the data
samples_w <- mod_WeightedBayes$sample( 
  data = list(
  N = nrow(dataWeightedBayesParam),
  S = 1,
  outcome = as.matrix(dataWeightedBayesParam$outcome),
  Source1 = as.matrix(dataWeightedBayesParam$Source1),
  Source2 = as.matrix(dataWeightedBayesParam$Source2),
  bias = as.matrix(dataWeightedBayesParam$bias)
),

  seed = 123,
  chains = 2,
  parallel_chains = 2,
  threads_per_chain = 2,
  iter_warmup = 1500,
  iter_sampling = 3000,
  refresh = 0,
  max_treedepth = 10,
  adapt_delta = 0.99
      )
   
  draws_df_param_recov_w2 <- as_draws_df(samples_w$draws()) 
  temp_paramw2 <- tibble(
                   w2EstScaled = inv_logit_scaled(draws_df_param_recov_w2$`w2[1]`), 
                   w2True = weightLvl2, 
                   w2Est = draws_df_param_recov_w2$`w2[1]`
                   )
    
    
    if (exists("parameter_recovery_dfw2")) {parameter_recovery_dfw2 <- rbind(parameter_recovery_dfw2, temp_paramw2)} else {parameter_recovery_dfw2 <- temp_paramw2}
    
  }
  
```


```{r}
# parameter recovery plot
w1 <- ggplot(parameter_recovery_dfw1, aes(w1True, w1Est)) +
  geom_point(alpha = 0.1) +
  geom_smooth(method = "lm", color = "purple") +
  xlab("True ω1")+
  ylab("Estimated ω1")+
  ggtitle("Weight1 from the Weighted Bayes Model")+
  theme_classic()  

w2 <- ggplot(parameter_recovery_dfw2, aes(w2True, w2Est)) +
  geom_point(alpha = 0.1) +
  geom_smooth(method = "lm", color = "red") +
  xlab("True ω2")+
  ylab("Estimated ω2")+
  ggtitle("Weight2 from the Weighted Bayes Model")+
  theme_classic()  

bias <- ggplot(parameter_recovery_dfbw, aes(biasTrue, biasEstScaled)) +
  geom_point(alpha = 0.1) +
  geom_smooth(method = "lm", color = "orange") +
  xlab("True β")+
  ylab("Estimated β")+
  ggtitle("Bias from the Weighted Bayes Model")+
  theme_classic()  

w1 + w2 + bias  + plot_layout(ncol = 1) + plot_annotation(title = "Parameter Recovery Weighted Bayes Model", theme = theme(plot.title = element_text(size = 20, hjust = 0.5)))
```



```{r}
# load empirical data
skidata <- read_csv("/Users/kristian/Documents/Skole/8. Semester/Data Science/Exam/DataScienceSkiDecisionMaking/skidata.csv")

# get avi and terrain into probability space (/n+1)
skidata$Source1 <- skidata$AvalancheConditions / 7  # n is 6
skidata$Source2 <- skidata$TerrainCharacteristics / 5 # n is 4

# get sources within scope for working with log-odds (i.e., avoid 0 and 1)
skidata$Source1 <- ifelse(skidata$Source1 == 0, 0.01, 
                  ifelse(skidata$Source1 == 1, 0.99, skidata$Source1))  # i.e., hardcode 0 to be 0.01 and 1 to be 0.99

skidata$Source2 <- ifelse(skidata$Source2 == 0, 0.01, 
                  ifelse(skidata$Source2 == 1, 0.99, skidata$Source2))  # i.e., hardcode 0 to be 0.01 and 1 to be 0.99
```


```{r}
### wrangle the data and fit it to the model ###
# pivot data wider
sim_wide_ski <- skidata %>% 
  group_by(id) %>% 
  subset(select = c(id, outcome, Source1, Source2)) %>%
  mutate(row = row_number()) %>% 
  pivot_wider(names_from = id, values_from = c(outcome, Source1, Source2))

# subject A
dataSimpleBayesSkiDre <- sim_wide_ski %>% 
  subset(select = c(outcome_2, Source1_2, Source2_2)) %>% 
  na.omit()

dataSimpleBayesSkiDre <- list(
  N = nrow(dataSimpleBayesSkiDre),
  S = 1,
  outcome = as.matrix(dataSimpleBayesSkiDre[,1]),
  Source1 = as.matrix(dataSimpleBayesSkiDre[,2]),
  Source2 = as.matrix(dataSimpleBayesSkiDre[,3])
)

# feed R the stan model
file <- file.path("weightedBayes.stan")
mod_simpleBayesSki <- cmdstan_model(file, cpp_options = list(stan_threads = TRUE),
                     stanc_options = list("O1"))

   
# create samples from the model
samples_simple_w_skiDre <- mod_simpleBayesSki$sample(
  data = dataSimpleBayesSkiDre,
  seed = 123,
  chains = 2,
  parallel_chains = 2,
  threads_per_chain = 2,
  iter_warmup = 1500,
  iter_sampling = 3000,
  refresh = 500
)


# get the resulting data frame
draws_df_ski_Dre <- as_draws_df(samples_simple_w_skiDre$draws())
```

```{r}
# Johan subject B
dataSimpleBayesSkiJoe <- sim_wide_ski %>% 
  subset(select = c(outcome_1, Source1_1, Source2_1)) %>% 
  na.omit()

dataSimpleBayesSkiJoe <- list(
  N = nrow(dataSimpleBayesSkiJoe),
  S = 1,
  outcome = as.matrix(dataSimpleBayesSkiJoe[,1]),
  Source1 = as.matrix(dataSimpleBayesSkiJoe[,2]),
  Source2 = as.matrix(dataSimpleBayesSkiJoe[,3])
)


# feed R the stan model
file <- file.path("weightedBayes.stan")
mod_simpleBayesSki <- cmdstan_model(file, cpp_options = list(stan_threads = TRUE),
                     stanc_options = list("O1"))
   
# create samples from the model
samples_simple_w_skiJoe <- mod_simpleBayesSki$sample(
  data = dataSimpleBayesSkiJoe,
  seed = 123,
  chains = 2,
  parallel_chains = 2,
  threads_per_chain = 2,
  iter_warmup = 1500,
  iter_sampling = 3000,
  refresh = 500
)

# get the resulting data frame
draws_df_ski_Joe <- as_draws_df(samples_simple_w_skiJoe$draws())
```

```{r}
# basic evaluation
samples_simple_w_skiJoe$cmdstan_diagnose()
samples_simple_w_skiDre$cmdstan_diagnose()

# diagnostics
summaryJoe <- samples_simple_w_skiJoe$summary()
samples_simple_w_skiJoe$loo()

summaryDre <- samples_simple_w_skiDre$summary()
samples_simple_w_skiDre$loo()

```

```{r}
# do the chains mix well?
p1wJoe <- ggplot(draws_df_ski_Joe, aes(.iteration, `bias[1]`, group = .chain, color = .chain)) +
  geom_line(alpha = 0.5) +
  theme_classic()
p1wDre <- ggplot(draws_df_ski_Dre, aes(.iteration, `bias[1]`, group = .chain, color = .chain)) +
  geom_line(alpha = 0.5) +
  theme_classic()
p1wJoe
p1wDre
```


```{r}
### parameter estimations plot used in paper ###
# bias Subject A plot
DreWb <- ggplot(draws_df_ski_Dre) +
  geom_density(aes(`bias_posterior[1]`), alpha = 0.6, fill = "lightblue") +
 # xlim(0,1)+
    annotate("text", colour = "lightblue", x = 0.01, y = 45, label = "Posterior Distribution β" , hjust = 0)+
  geom_density(aes(`bias_prior[1]`), alpha = 0.6, fill = "pink") +
    annotate("text", colour = "pink", x = 0.01, y = 37, label = "Prior Distribution β", hjust =0)+
  xlab("β")+
  ylab("Estimated β Densitites")+
  theme_classic()+
  geom_vline(xintercept = mean(db$bias), linetype = "dashed", size = 1.5) +
    annotate("text", x = 0.01, y = 28,  label="Simulated β", hjust = 0)+
  geom_vline(xintercept = summaryDre$q5[37], linetype = "solid", color = "grey", size = 0.5, alpha = 1)+
  geom_vline(xintercept = summaryDre$q95[37], linetype = "solid", color = "grey", size = 0.5, alpha = 1)+
  geom_rect(aes(xmin = 0, xmax = 0.3, ymin = 25, ymax = 48), 
            fill = "white", color = "black", alpha = 0)+
  ggtitle("Subject A")



# bias Subject B plot
JoeWb <- ggplot(draws_df_ski_Joe) +
  geom_density(aes(`bias_posterior[1]`), alpha = 0.6, fill = "lightblue") +
 # xlim(0,1)+
    annotate("text", colour = "lightblue", x = 0.01, y = 45, label = "Posterior Distribution β" , hjust = 0)+
  geom_density(aes(`bias_prior[1]`), alpha = 0.6, fill = "pink") +
    annotate("text", colour = "pink", x = 0.01, y = 37, label = "Prior Distribution β", hjust =0)+
  xlab("β")+
  ylab("Estimated β Densitites")+
  theme_classic()+
  geom_vline(xintercept = mean(db$bias), linetype = "dashed", size = 1.5) +
    annotate("text", x = 0.01, y = 28,  label="Simulated β", hjust = 0)+
  geom_vline(xintercept = summaryJoe$q5[25], linetype = "solid", color = "grey", size = 0.5, alpha = 1)+
  geom_vline(xintercept = summaryJoe$q95[25], linetype = "solid", color = "grey", size = 0.5, alpha = 1)+
  geom_rect(aes(xmin = 0, xmax = 0.3, ymin = 25, ymax = 48), 
            fill = "white", color = "black", alpha = 0)+
  ggtitle("Subject B")


# weight 1 subject A plot
DreW1 <- ggplot(draws_df_ski_Dre) +
  geom_density(aes(`w1_posterior[1]`), alpha = 0.6, fill = "lightblue") +
  xlim(0,1)+
    annotate("text", colour = "lightblue", x = 0.01, y = 45, label = "Posterior Distribution β" , hjust = 0)+
  geom_density(aes(`w1_prior[1]`), alpha = 0.6, fill = "pink") +
    annotate("text", colour = "pink", x = 0.01, y = 37, label = "Prior Distribution β", hjust =0)+
  xlab("ω1")+
  ylab("Estimated ω1 Densitites")+
  theme_classic()+
  geom_vline(xintercept = mean(db$w1), linetype = "dashed", size = 1.5) +
    annotate("text", x = 0.01, y = 28,  label="Simulated β", hjust = 0)+
  geom_vline(xintercept = summaryDre$q5[40], linetype = "solid", color = "grey", size = 0.5, alpha = 1)+
  geom_vline(xintercept = summaryDre$q95[40], linetype = "solid", color = "grey", size = 0.5, alpha = 1)+
  geom_rect(aes(xmin = 0, xmax = 0.3, ymin = 25, ymax = 48), 
            fill = "white", color = "black", alpha = 0)+
  ggtitle("Subject A")


# weight 1 Subject B plot
JoeW1 <- ggplot(draws_df_ski_Joe) +
  geom_density(aes(`w1_posterior[1]`), alpha = 0.6, fill = "lightblue") +
  xlim(0,1)+
    annotate("text", colour = "lightblue", x = 0.01, y = 45, label = "Posterior Distribution β" , hjust = 0)+
  geom_density(aes(`w1_prior[1]`), alpha = 0.6, fill = "pink") +
    annotate("text", colour = "pink", x = 0.01, y = 37, label = "Prior Distribution β", hjust =0)+
  xlab("ω1")+
  ylab("Estimated ω1 Densitites")+
  theme_classic()+
  geom_vline(xintercept = mean(db$w1), linetype = "dashed", size = 1.5) +
    annotate("text", x = 0.01, y = 28,  label="Simulated β", hjust = 0)+
  geom_vline(xintercept = summaryJoe$q5[28], linetype = "solid", color = "grey", size = 0.5, alpha = 1)+
  geom_vline(xintercept = summaryJoe$q95[28], linetype = "solid", color = "grey", size = 0.5, alpha = 1)+
  geom_rect(aes(xmin = 0, xmax = 0.3, ymin = 25, ymax = 48), 
            fill = "white", color = "black", alpha = 0)+
  ggtitle("Subject B")
  

# weight 2 subject A
DreW2 <- ggplot(draws_df_ski_Dre) +
  geom_density(aes(`w2_posterior[1]`), alpha = 0.6, fill = "lightblue") +
  xlim(0,1)+
    annotate("text", colour = "lightblue", x = 0.01, y = 45, label = "Posterior Distribution β" , hjust = 0)+
  geom_density(aes(`w2_prior[1]`), alpha = 0.6, fill = "pink") +
    annotate("text", colour = "pink", x = 0.01, y = 37, label = "Prior Distribution β", hjust =0)+
  xlab("Bias")+
  ylab("Estimated ω2 Densitites")+
  theme_classic()+
  geom_vline(xintercept = mean(db$w2), linetype = "dashed", size = 1.5) +
    annotate("text", x = 0.01, y = 28,  label="Simulated β", hjust = 0)+
  geom_vline(xintercept = summaryDre$q5[41], linetype = "solid", color = "grey", size = 0.5, alpha = 1)+
  geom_vline(xintercept = summaryDre$q95[41], linetype = "solid", color = "grey", size = 0.5, alpha = 1)+
  geom_rect(aes(xmin = 0, xmax = 0.3, ymin = 25, ymax = 48), 
            fill = "white", color = "black", alpha = 0)+
  ggtitle("Subject A")


# weight 2 subject B plot
JoeW2 <- ggplot(draws_df_ski_Joe) +
  geom_density(aes(`w2_posterior[1]`), alpha = 0.6, fill = "lightblue") +
  xlim(0,1)+
    annotate("text", colour = "lightblue", x = 0.01, y = 45, label = "Posterior Distribution β" , hjust = 0)+
  geom_density(aes(`w2_prior[1]`), alpha = 0.6, fill = "pink") +
    annotate("text", colour = "pink", x = 0.01, y = 37, label = "Prior Distribution β", hjust =0)+
  xlab("ω2")+
  ylab("Estimated ω2 Densitites")+
  theme_classic()+
  geom_vline(xintercept = mean(db$w2), linetype = "dashed", size = 1.5) +
    annotate("text", x = 0.01, y = 28,  label="Simulated β", hjust = 0)+
  geom_vline(xintercept = summaryJoe$q5[29], linetype = "solid", color = "grey", size = 0.5, alpha = 1)+
  geom_vline(xintercept = summaryJoe$q95[29], linetype = "solid", color = "grey", size = 0.5, alpha = 1)+
  geom_rect(aes(xmin = 0, xmax = 0.3, ymin = 25, ymax = 48), 
            fill = "white", color = "black", alpha = 0)+
  ggtitle("Subject B")
  

weights1Emp <-   (DreW1|JoeW1)
weights2Emp <- (DreW2| JoeW2)
biasEmp <- (DreWb|JoeWb)

all_param <- ggarrange(weights1Emp, weights2Emp, biasEmp, ncol = 1, nrow = 3)

annotate_figure(all_param, top = text_grob("Prior Posterior Updates for the Weighted Bayes Parameters", 
              face = "bold", size = 30))


#png(filename = "/Users/kristian/Documents/Skole/8. Semester/Data Science/Exam/DataScienceSkiDecisionMaking/all_param_update.png")

#dev.off()
```


